### 2025-04-16 correlation.qmd
20250415 - update packages

An example of a nonlinear correlation is a distance correlation and the xi ($\xi$) coefficient.
These estimates of nonlinear correlation only range from 0–1 (where 0 represents no association and 1 represents a strong association), so they are interpreted differently than a traditional correlation coefficient (which can be negative).
We can estimate a distance correlation using the `correlation()` function of the correlation package [@R-correlation; @Makowski2020].

@@

One approach is the biweight midcorrelation, which is based on the median rather than the mean, and is thus less sensitive to outliers.
Another approach is the percentage bend correlation, which gives less weight to observations that are farther away from the median.
We can estimate the each using the `correlation()` function of the correlation package [@R-correlation; @Makowski2020].

>>>>

An example of a nonlinear correlation is a distance correlation and the xi ($\xi$) coefficient.
These estimates of nonlinear correlation only range from 0–1 (where 0 represents no association and 1 represents a strong association), so they are interpreted differently than a traditional correlation coefficient (which can be negative).
We can estimate a distance correlation using the `correlation()` function of the correlation package [@R-correlation; @Makowski2020_packages].

@@

One approach is the biweight midcorrelation, which is based on the median rather than the mean, and is thus less sensitive to outliers.
Another approach is the percentage bend correlation, which gives less weight to observations that are farther away from the median.
We can estimate the each using the `correlation()` function of the correlation package [@R-correlation; @Makowski2020_packages].

### 2025-04-16 multiple-regression.qmd
20250415 - fix
20250415 - update packages

We can also evaluate residual plots (@fig-residualPlots), marginal model plots (@fig-marginalModelPlots), and added-variable plots (@fig-addedVariablePlots) from the `car` package [@Fox2019; @R-car], to evaluate for potential nonlinearity.
For evaluating linearity, we would expect minimal bend/curvature in the lines.

@@

To determine if residuals are correlated given the nested structure of the data, we can examine the proportion of variance that is attributable to the particular player.
To do this, we can estimate the intraclass correlation coefficient (ICC) from a [mixed model](#sec-mixedModels) using the `performance` package [@Ludecke2021; @R-performance].

@@

We can estimate a regression model that uses pairwise deletion using the `lavaan` package [@Rosseel2012; @R-lavaan].

@@

We can multiply impute data using the `mice` package [@vanBuuren2011; @R-mice].

@@

We can estimate a regression model that uses full information maximum likelihood using the `lavaan` package [@Rosseel2012; @R-lavaan].

@@

A mediation model takes the following general form in the `lavaan` package [@Rosseel2012; @R-lavaan].

@@

  fantasyPoints_transformed ~ b1*receiving_tds + b1*receiving_yards

>>>>

We can also evaluate residual plots (@fig-residualPlots), marginal model plots (@fig-marginalModelPlots), and added-variable plots (@fig-addedVariablePlots) from the `car` package [@Fox2019_packages; @R-car], to evaluate for potential nonlinearity.
For evaluating linearity, we would expect minimal bend/curvature in the lines.

@@

To determine if residuals are correlated given the nested structure of the data, we can examine the proportion of variance that is attributable to the particular player.
To do this, we can estimate the intraclass correlation coefficient (ICC) from a [mixed model](#sec-mixedModels) using the `performance` package [@Ludecke2021_packages; @R-performance].

@@

We can estimate a regression model that uses pairwise deletion using the `lavaan` package [@Rosseel2012_packages; @R-lavaan].

@@

We can multiply impute data using the `mice` package [@vanBuuren2011_packages; @R-mice].

@@

We can estimate a regression model that uses full information maximum likelihood using the `lavaan` package [@Rosseel2012_packages; @R-lavaan].

@@

A mediation model takes the following general form in the `lavaan` package [@Rosseel2012_packages; @R-lavaan].

@@

  fantasyPoints_transformed ~ b1*receiving_tds + b2*receiving_yards
